### 2024-06-07 project_Julio/paper.tex
commit4_1

Based on the previous work on the Run 2 (2015-2016) datasets which have achieved a uncertainty of  2.3\% \cite{Collaboration:121}, we expect that a precision at 2\% will be possible due to the improved methods we are developing.
For reference, the current systematic uncertainty on the Run 2 2017 was 2.3\% \cite{Collaboration:122} for 2018 was 2.5\% \cite{Collaboration:123} and for Run 3 (2022) was 1.4\% \cite{Collaboration:124}.

@@

\newpage
\onehalfspacing
\bibliographystyle{unsrt}
\bibliography{paper}

>>>>

Based on the previous work on the Run 2 (2015-2016) datasets which have achieved a uncertainty of  2.3\% \cite{Collaboration:121}, we expect that a precision at 2\% will be possible due to the improved methods we are developing.
For reference, the current systematic uncertainty on the Run 2 2017 was 2.3\% \cite{CMS:2018elu} for 2018 was 2.5\% \cite{CMS:2018} and for Run 3 (2022) was 1.4\% \cite{Collaboration:124}.

@@

\newpage
\onehalfspacing
\bibliographystyle{plain}
\bibliography{paper}
